---
title: "Pre-workshop instructions"
---

Please make sure to bring a laptop with you to the workshop and complete the following steps:

## Software

Download and install the latest versions of R, RStudio, and Quarto:

-   R 4.2.3 or above: <https://cran.r-project.org>

-   RStudio 2023.09.1+494 or above: <https://posit.co/download/rstudio-desktop>

-   Quarto 1.3.450: <https://quarto.org/docs/get-started>

## R Packages 

Install the following packages:

```{r}
#| eval: false

pkg_list <- c("tidyverse", "gt", "ggthemes", "palmerpenguins", "quarto", "here", "usethis")
install.packages(pkg_list)
```

## Exercises

Download and open the exercises for this session. The easiest way is to run this line of R code at the console in RStudio.

```{r}
#| eval: false

usethis::use_course("https://bit.ly/wsds-exercises")
```

If that doesn't work, you can download a zip file of the exercises [here](https://github.com/mine-cetinkaya-rundel/quarto-wsds-exercises), then open the directory. The qmd files can be opened in RStudio.
